Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-28 rates-neurips-21/rates.tex
lit review for rates -- yikes that took a long time

\raf{Basic outline, to flesh out tomorrow!}
\begin{itemize}
\item It all started with binary classification (Zhang), where we know the most.  Bartlett gave a nice closed form expression for $\zeta$ for margin losses, and Reid+W for the mostly broader class of composite proper losses.  So we have tight $\zeta$ functions for nearly every consistent surrogate.
\item By extension, we know a lot about close variants of binary classification, like cost-sensitive binary classification, binary classification with an abstain option~\cite{bartlett2008classification}, and bipartite ranking.
\item The next step is multiclass classification, yet commonly-used surrogates are actually not consistent.  For example, the common practice of one-versus-all hinge loss is actually consistent for multiclass classification with an abstain option; \citet{ramaswamy2018consistent} give a linear surrogate regret bound for this polyhedral surrogate, as well as two others for the same problem.  Related: hierarchical classification, which also has a polyhedral surrogate and linear regret bound.  Our results would have greatly simplified the development of these regret bounds; we describe how to recover the main BEP bound in \S.
\item Finally, structured prediction be pumpin out surrogates.... general results... but usually quadratic losses.  Show lower bounds like our Thm 2 in those two papers.
\end{itemize}

~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}

Surrogate regret bounds have been well studied in some settings.
It is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.

% 1. super general
% 2. lower bound could explain why you get sqrt or linear
%   - take exp: not strong convex or strong smooth, so why sqrt??
% 3. polyhedral pipeline

Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  $\leq$ = gives a ``lower bound'' for the surrogate regret too.
\begin{itemize}
\item Binary classification.
  \begin{itemize}
  \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
  \item \citet{bartlett2006convexity} -- tight bounds for \textbf{all margin losses}
  \item \citet{reid2009surrogate} -- tight bounds for \textbf{all proper composite losses}
  \item \citet{mahdavi2014binary} -- consider the generalization rate of the surrogate together with the ``excess risk bound'' (surrogate regret bound) (\textbf{and} the optimization actually), both as a function of the smoothness parameter of the surrogate.  They don't seem to give lower bounds on the excess risk bound though, just a degrading upper bound on it.  Still, very close to our work (and more generally the ``full stack'' idea!) in spirit.
  \end{itemize}

\item Weighted / cost-sensitive variants
  \begin{itemize}
  \item \citet{scott2011surrogate} -- weird example-dependent problem
  \item \citet{scott2012calibrated} -- general cost-sensitive binary classification
  \end{itemize}

\item Bipartite ranking (which is basically a set of pairwise binary classifications)
  \begin{itemize}
  \item \citet{agarwal2014surrogate} -- builds on binary classification losses (Mark + Bob), introduces strongly proper
  \item \citet{menon2016bipartite} -- different sort of regret bound, same problem
  \end{itemize}

\item Abstain and hierarchical
  \begin{itemize}
  \item[P,L] \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all \textbf{linear}, each ``from scratch''.
  \item[Q] \citet{yuan2010classification} -- Smooth? losses and characterizations for abstain; \textbf{binary classification only}
  \item[P,L] \citet{bartlett2008classification} -- The OG abstain paper, with a polyhedral hinge-like loss.  \textbf{Linear} regret bound.
  \item[P,L] \citet{ramaswamy2015hierarchical} -- Nested OvA surrogate; linear bound
  \end{itemize}

\item Ordinal regression
  \begin{itemize}
  \item \citet{pedregosa2017consistency} -- Pretty fascinating paper actually, about ordinal regression, i.e., when the label is the ordinal rank of the outcome, and how to construct surrogates.  For a class of surrogates based on binary classification, which is also cool, they get similar excess risk bounds to \citet{bartlett2006convexity}.
  \end{itemize}

\item List ranking
  \begin{itemize}
  \item[Q] \citet[Theorem 10]{ravikumar2011ndcg}
  \end{itemize}

\item Structured prediction (covering lots of target problems simultaneously)
  \begin{itemize}
  \item[Q,$\leq$] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.  Also give an upper bound on the calibration function, i.e. a lower bound in the sense that we prove (Theorem 8).
  \item[Q] \citet{ciliberto2016consistent} -- Calibration function for a similar quadratic surrogate, for a similarly general class of structed pred problems.
  \item[Q,$\leq$] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g. includes ordinal regression).  Quadratic risk bound for a proper loss for the mean from a strongly-convex potential/entropy.
    Also give a matching lower bound in our sense (Theorem 4.5).
  \item[Q] \citet[Proposition 5]{blondel2019structured} -- Tighter losses, still quadratic, still quadratic excess risk.
  \end{itemize}

\item Polyhedral surrogates without risk/regret bounds
  \begin{itemize}
  \item \citet{wang2020weston} -- Weston--Watkins: calibrated for ordered partition
  \item \citet{yu2018lovasz} -- Lov\'asz hinge: calibrated for an abstain-like loss (from our paper)
  \item Top-$k$ losses, like \citet{lapin2016loss} and any others from \citet{yang2018consistency}
  \end{itemize}

\item Fast rates
  \begin{itemize}
  \item \citet{koren2015fast} -- fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) .  Note here exp-concavex is in the \emph{parameter}.  So $F(\theta) = L(h_\theta(x),y)$ should be exp-concave in $\theta$.  For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
  \item \citet{grunwald2015fast} -- Tim et al paper than Anish referenced!  
  \end{itemize}

\item Misc / didn't read
  \begin{itemize}
  \item Excess Risk Bounds for Exponentially Concave Losses \url{https://arxiv.org/pdf/1401.4566.pdf}
  \end{itemize}
\end{itemize}

>>>>

Surrogate regret bounds were perhaps developed first by \citet{zhang2004statistical}, as a method to prove statistical consistency for various surrogate losses for binary classification.
These results were then generalized by \citet{bartlett2006convexity} for margin losses, and \citet{reid2009surrogate} for composite proper losses.
These latter works and others give a fairly complete picture for binary classification: a characterization of calibrated surrogates, and precise closed forms for the optimal $\zeta$ for each.
By extension, close variations on binary classification are also well-understood, such as  cost-sensitive binary classification~\citep{scott2012calibrated}, binary classification with an abstain option~\citep{bartlett2008classification,yuan2010classification}, bipartite ranking~\citep{agarwal2014surrogate,menon2016bipartite}, and ordinal regression via reduction to binary classification~\citep{pedregosa2017consistency}.
For multiclass classification, we have nice consistency characterizations with respect to 0-1 loss~\citep{tewari2007consistency}, with some surrogate regret bounds~\citep{pires2013cost,duchi2018multiclass}.

Beyond binary classification and 0-1 loss, our knowledge drops off precipitously, with few general results.
There are some works which provide partial understand for specific target problems.
For example, in the problem of multiclass classification with an abstain option, \citet{ramaswamy2018consistent} give three consistent polyhedral surrogates (two of which are commonly used as inconsistent surrogates for 0-1 loss), along with linear surrogate regret bounds.
\citet{ramaswamy2015hierarchical} show how to extend these surrogates to nested, hierarchical versions, again providing linear regret bounds.
Motivated by these polyhedral surrogates, together with examples arising in top-$k$ prediction~\citep{lapin2016loss,yang2018consistency} and other structured prediction problems~\citep{yu2018lovasz}, \citet{finocchiaro2019embedding} introduce an embedding framework for polyhedral surrogates.
This framework shows that all polyhedral surrogates are consistent for some discrete target problem, and vice versa, but do not provide surrogate regret bounds.
Our results fill this gap, giving linear regret bounds for all polyhedral losses, and thus all discrete target problems.

Perhaps closest in spirit to our work are several recent works on general structured prediction problems.
\citet[Theorem 2]{ciliberto2016consistent} and \citet[Theorem 7]{osokin2017structured} give surrogate regret bounds for a quadratic surrogate, for a general class of structed prediction problems.
\citet[Proposition 5]{blondel2019structured} gives surrogate regret bounds for a tighter class of quadratic surrogates based on projection oracles.
\citet[Theorem 4.4]{nowak2019general} give even more general bounds, using a broader class of surrogates based on estimating a vector-valued expectation.
All of these works apply to a broad range of discrete target problems.
The main difference to our work is that their upper bounds are all for strongly convex surrogates,%
\footnote{These works express surrogate regret bounds with $\zeta^{-1}$ appearing on the left-hand side of eq.~\eqref{eq:surrogate-regret-bound-informal}, and thus the terms ``upper bound'' and ``lower bound'' are opposite from their terminology.}
whereas ours are for polyhedral surrogates.
\citet[Theeorem 8]{osokin2017structured} and \citet[Theorem 4.5]{nowak2019general} also provide lower bounds, in the same spirit as our Theorem~\ref{thm:main-lower} but only for the classes of surrogates they study.
In particular, our results recover their bounds up to a constant factor.
